Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 problem_setting.tex

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
Notice that based on Assumption~\ref{A1} below,
  \Best{\AgV} and \Second{\AgV} are unique with probability 1.
\pfcomment{Why is \Second{\AgV} unique with probability 1?  I don't think that is implied.  Can I remove that part of the statement?}
\dkcomment{It is unique with probablity 1 over the draw of agent types
  because for z=0, Assumption~\ref{A1} says that there is a measure 0
  set of agents whose difference between the best and second-best
  option is z=0. Or am I misunderstanding something?}
  \pfcomment{That argument says that $\Best{\AgV}$ is unique.  But the second best, $\Second{\AgV}$, doesn't have to be.  The measure of the set of agents with 0 gap between the second- and third-best  options might not vanish.}

>>>>

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
Notice that based on Assumption~\ref{A1} below,
\dkedit{\Best{\AgV} is unique with probability 1.}
